Empirical Analysis of the Role of Energy in Economic Growth

### 2013-01-27 EconGrowth.Rnw
Now creating a table for all CD countries. Unfortunately, I have one additional column (don't know why), and there are way too many significant figures in the table. The digit=c() parameter doesn't seem to be working yet.

# Statistical significance levels. We'll work with 95% CIs
ciLevel <- 0.95
ciHalfLevel <- ciLevel + (1.0-ciLevel)/2.0
# List of countries
countries <- c(US="US", UK="UK", JP="JP", ZA = "ZA", CN="CN", IR="IR", SA="SA", TZ="TZ", ZM="ZM")
# List of energy types
energyTypes <- c(Q = "Q", X = "X", U = "U")
@

@@

<<Factors of Production Lattice Graph, fig.width=6.5, fig.height=7.5, fig.cap="Factors of Production for All Countries. (China's indexed capital stock rises to $k = 9.2$ in 2011.)", echo=FALSE>>=
createFactorsLatticeGraph <- function(countryName){
  dataTable <- loadData(countryName)
  graphType <- "l"
  lineTypes <- c(1, 5, 2, 4, 6) #line types. See http://en.wikibooks.org/wiki/R_Programming/Graphics
  lineWidths <- c(1, 1, 1, 1, 1) #line widths
  colors <- c("black", "black", "black", "black", "black") #line and point colors
  lineSpec <- list(lty=lineTypes, lwd=lineWidths, col=colors)
  graph <- xyplot(iCapStk+iLabor+iQ+iX+iU ~ Year | Country, data=dataTable,
                  index.cond=list(c(7,6,3,1,8,5,4,2,9)), #orders the panels. Default is alphabetical.
                  as.table=TRUE,
                  type=graphType,
                  layout=c(3,3),
                  par.settings = list(superpose.line = lineSpec),
                  key=list(text=list(c("k", "l", "q", "x", "u")),
                           type=graphType,
                           cex=0.85,
                           lines=lineSpec,
                           columns=1, x=0.01, y=0.95),
                  scales=list(cex=0.75, #controls text size on scales
                              tck=-0.5, #controls tick mark length
                              y=list(at=c(1,2,3,4,5,6,7,8,9,10))), 
                  xlab="",
                  ylim=c(0.5,4.5),
                  ylab="Indexed (1980=1 or 1991=1)")
  return(graph)
}
createFactorsLatticeGraph("All") #Reads data from the "AllData.txt" file.
@

<<graphs>>=
createCountryFactorsGraph <- function(countryName){
  dataTable <- loadData(countryName)
  graphType <- "l"
  lineTypes <- c(1, 5, 2, 4, 6) #line types. See http://en.wikibooks.org/wiki/R_Programming/Graphics
  lineWidths <- c(1, 1, 1, 1, 1) #line widths
  colors <- c("black", "black", "black", "black", "black") #line and point colors
  lineSpec <- list(lty=lineTypes, lwd=lineWidths, col=colors)
  graph <- xyplot(iCapStk+iLabor+iQ+iX+iU ~ Year, data=dataTable,
                  type=graphType,
                  par.settings = list(superpose.line = lineSpec),
                  key=list(text=list(c("k", "l", "q", "x", "u")),
                           type=graphType,
                           lines=lineSpec,
                           columns=1, x=0.0, y=0.98),
                  scales=list(cex=1.0, #controls text size on scales
                              tck=-0.5), #controls tick mark length
                  ylab="Indexed (1980=1)")
  return(graph)
}

@@

####################################
# Creates a LaTeX printable table from the Cobb Douglas data. This function first calls cobbDouglasData.
#
# countryName is a string containint the 2-letter abbreviation for the country, e.g. "US" or "CN"
#
# returns a printable LaTeX table from xtable.
##
cobbDouglasTable <- function(countryName){
  dataCD <- cobbDouglasData(countryName) 
  colnames(dataCD) <- c("$\\lambda$", "$\\alpha$", "$\\beta$", "$\\gamma$")
  tableCD <- xtable(dataCD, caption=paste(countryName, " Cobb-Douglas, 1980-2011", sep=""), digit = c(4, 4, 2, 2, 1))
  #print(tableCD)
  return(tableCD)  
}
@

<<CD Analysis>>=
tablesCD <- lapply(countries, cobbDouglasTable)
@

<<CD Results, results='asis'>>=
print(tablesCD[["US"]], caption.placement="top")
print(tablesCD[["UK"]], caption.placement="top")
print(tablesCD[["JP"]], caption.placement="top")
print(tablesCD[["ZA"]], caption.placement="top")
print(tablesCD[["CN"]], caption.placement="top")
print(tablesCD[["SA"]], caption.placement="top")
print(tablesCD[["IR"]], caption.placement="top")
print(tablesCD[["TZ"]], caption.placement="top")
print(tablesCD[["ZM"]], caption.placement="top")

>>>>

# Statistical significance levels. We'll work with 95% CIs
ciLevel <- 0.95
ciHalfLevel <- ciLevel + (1.0-ciLevel)/2.0
# List of countries
countries <- c(US="US", UK="UK", JP="JP", CN="CN", ZA = "ZA", SA="SA", IR="IR", TZ="TZ", ZM="ZM")
# List of energy types
energyTypes <- c(Q = "Q", X = "X", U = "U")
@

@@

<<Factors Lattice Graph, fig.width=6.5, fig.height=7.5, fig.cap="Factors of Production for All Countries. (China's indexed capital stock rises to $k = 9.2$ in 2011.)", echo=FALSE>>=
createFactorsLatticeGraph <- function(countryName){
  dataTable <- loadData(countryName)
  graphType <- "l"
  lineTypes <- c(1, 5, 2, 4, 6) #line types. See http://en.wikibooks.org/wiki/R_Programming/Graphics
  lineWidths <- c(1, 1, 1, 1, 1) #line widths
  colors <- c("black", "black", "black", "black", "black") #line and point colors
  lineSpec <- list(lty=lineTypes, lwd=lineWidths, col=colors)
  graph <- xyplot(iCapStk+iLabor+iQ+iX+iU ~ Year | Country, data=dataTable,
                  index.cond=list(c(7,6,3,1,8,5,4,2,9)), #orders the panels. Default is alphabetical.
                  as.table=TRUE,
                  type=graphType,
                  layout=c(3,3),
                  par.settings = list(superpose.line = lineSpec),
                  key=list(text=list(c("k", "l", "q", "x", "u")),
                           type=graphType,
                           cex=0.85,
                           lines=lineSpec,
                           columns=1, x=0.01, y=0.95),
                  scales=list(cex=0.75, #controls text size on scales
                              tck=-0.5, #controls tick mark length
                              y=list(at=c(1,2,3,4,5,6,7,8,9,10))), 
                  xlab="",
                  ylim=c(0.5,4.5),
                  ylab="Indexed (1980=1 or 1991=1)")
  return(graph)
}
createFactorsLatticeGraph("All") #Reads data from the "AllData.txt" file.
@

<<Country Factors Graph>>=
createCountryFactorsGraph <- function(countryName){
  dataTable <- loadData(countryName)
  graphType <- "l"
  lineTypes <- c(1, 5, 2, 4, 6) #line types. See http://en.wikibooks.org/wiki/R_Programming/Graphics
  lineWidths <- c(1, 1, 1, 1, 1) #line widths
  colors <- c("black", "black", "black", "black", "black") #line and point colors
  lineSpec <- list(lty=lineTypes, lwd=lineWidths, col=colors)
  graph <- xyplot(iCapStk+iLabor+iQ+iX+iU ~ Year, data=dataTable,
                  type=graphType,
                  par.settings = list(superpose.line = lineSpec),
                  key=list(text=list(c("k", "l", "q", "x", "u")),
                           type=graphType,
                           lines=lineSpec,
                           columns=1, x=0.0, y=0.98),
                  scales=list(cex=1.0, #controls text size on scales
                              tck=-0.5), #controls tick mark length
                  ylab="Indexed (1980=1)")
  return(graph)
}

@@

############
# Creates a row for the Cobb Douglas parameters table
##
cobbDouglasCountryRow <- function(countryName){
  dataCD <- cobbDouglasData(countryName)
  # Create CI ranges
  out <- cbind(countryName, 
               dataCD["- 95% CI", "lambda"], dataCD["CD", "lambda"], dataCD["+ 95% CI", "lambda"],
               dataCD["- 95% CI", "alpha"],  dataCD["CD", "alpha"],  dataCD["+ 95% CI", "alpha"],
               dataCD["- 95% CI", "beta"],   dataCD["CD", "beta"],   dataCD["+ 95% CI", "beta"])

  return(out)
}

cobbDouglasParamsTable <- function(){
  dataCD <- rbind(cobbDouglasCountryRow("US"),
                cobbDouglasCountryRow("UK"),
                cobbDouglasCountryRow("JP"),
                cobbDouglasCountryRow("CN"),
                cobbDouglasCountryRow("ZA"),
                cobbDouglasCountryRow("SA"),
                cobbDouglasCountryRow("IR"),
                cobbDouglasCountryRow("TZ"),
                cobbDouglasCountryRow("ZM"))
  colnames(dataCD) <- c("", "-95% CI", "$\\lambda$", "+95% CI", 
                        "-95% CI", "$\\alpha$",  "+95% CI",
                        "-95% CI", "$\\beta$",   "+95% CI")
  rownames(dataCD) <- countries
  print("************** Trying to print dataCD **********************")
#   print(class(dataCD))
#   print(dataCD)
  tableCD <- xtable(dataCD, caption="Cobb-Douglas, 1980-2011 or 1991-2011", digit = c(1,1, 4,4,4, 4,4,4, 4,4,4))
  #print(tableCD)
  return(tableCD)
}
cobbDouglasParamsTable()

####################################
# Creates a LaTeX printable table from the Cobb Douglas data. This function first calls cobbDouglasData.
#
# countryName is a string containint the 2-letter abbreviation for the country, e.g. "US" or "CN"
#
# returns a printable LaTeX table from xtable.
##
cobbDouglasCountryTable <- function(countryName){
  dataCD <- cobbDouglasData(countryName) 
  colnames(dataCD) <- c("$\\lambda$", "$\\alpha$", "$\\beta$", "$\\gamma$")
  tableCD <- xtable(dataCD, caption=paste(countryName, " Cobb-Douglas, 1980-2011", sep=""), digit = c(4, 4, 2, 2, 1))
  #print(tableCD)
  return(tableCD)  
}
@

<<CD Analysis>>=
tablesCD <- lapply(countries, cobbDouglasCountryTable)
@

<<CD Results, results='asis', echo=FALSE>>=
print(cobbDouglasParamsTable(), caption.placement="top")

print(tablesCD[["US"]], caption.placement="top")
print(tablesCD[["UK"]], caption.placement="top")
print(tablesCD[["JP"]], caption.placement="top")
print(tablesCD[["CN"]], caption.placement="top")
print(tablesCD[["ZA"]], caption.placement="top")
print(tablesCD[["SA"]], caption.placement="top")
print(tablesCD[["IR"]], caption.placement="top")
print(tablesCD[["TZ"]], caption.placement="top")
print(tablesCD[["ZM"]], caption.placement="top")
